### 2017-12-08 UOW_thesis_template_v2-0/thesis_template/chapters/jumpImpVol.tex
:art: Jeff's changes before Marianito's help
:art: Changes from December 8

\subsection{Homogeneity of the solution}
First, we assume that the payoff function $\phi$ now depends on a parameter~$x' > 0$ (i.e., $\phi = \phi(x;x')$).  The motivation for this is that in the case of a European put or call, $x'$ represents the strike price. Furthermore, we assume that $\phi$ is homogeneous of degree one in~$x$ and $x'$. Note that standard put and call payoffs satisfy this assumption. We show that the option price function~$v$ is homogeneous of degree one in~$x$ and $x'$. That is, we want to show for $v = v(x,t; x')$ that
		\begin{equation}
			\label{eqn:homogen}
			v(\beta x, t; \beta x') = \beta v(x,t; x')
		\end{equation}
for all $\beta > 0$. This equality can be proven via a uniqueness argument as follows. We first express \eqref{eqn:PIDE} as $\mathscr{L} v = 0$. Now let $w = w(x,t; x')$ solve the following final value problem:
		\begin{align}
			\label{eqn:subPIDE}
			\begin{split}
			&\mathscr{L}w = 0, \qquad w(x,T; x') = \beta\phi(x;x').
			\end{split}
		\end{align}
Next, we define the function $v_1(x,t;x') = \beta v(x,t;x')$, where $v$ is a solution to (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Then
	\begin{align*}
		\mathscr{L}v_1 = \beta \mathscr{L}v = 0.
	\end{align*}
For the terminal condition, since $v(x,T;x') = \phi(x;x')$, this implies that
	\begin{equation*}
		v_1(x,T;x') = \beta v(x,T; x') = \beta\phi(x;x').
	\end{equation*}
Therefore $v_1$ satisfies the final value problem \eqref{eqn:subPIDE}. On the other hand, we now let $v_2(x,t,x') = v(\beta x, t; \beta x')$. Computing the derivatives gives
	\begin{equation*}
		\fr{\pr v_2}{\pr x} = \beta D_1v, \quad \fr{\pr^2 v_2}{\pr x^2} = \beta^2 D_{11}v,
	\end{equation*}
where $D_1$ and $D_{11}$ represent the first and second partial derivatives with respect to the first argument, respectively. Substituting these into (\ref{eqn:subPIDE}), we get
	\begin{align*}
		\mathscr{L}v_2 = \mathscr{L}v = 0,
	\end{align*}
and by the homogeneity of $\phi$, the terminal condition is
	\begin{align*}
		v_2(x,T;x') = v\left( \beta x, T; \beta x' \right) = \phi(\beta x; \beta x') = \beta \phi(x;x').
	\end{align*}
Hence $v_2$ also satisfies the final value problem \eqref{eqn:subPIDE}. By uniqueness, we have
	\begin{equation*}
		v\left(\beta x, t; \beta x'\right) = v_2(x,t;x') = v_1(x,t;x') = \beta v(x,t;x'),
	\end{equation*}
thus proving the homogeneity property for $v$ and any general payoff $\phi$ that is homogeneous of degree one in~$x$ and $x'$.

@@

\section{Implied volatility formula}
From (\ref{eqn:DupireLike}) and (\ref{eqn:DupireCond}), it is possible to now solve the inverse problem of implied volatility estimation. Throughout the remainder of this section, we will assume that~$r$, $q$, and $\sigma$ are constants. Suppose that we are given $u(x',0;S_0)$ for all $x' > 0$. We wish to derive an explicit formula for $\sigma$ in terms of certain integrals of $u$ with respect to $x'$. The reason for this is that in practice one can observe different time-zero option prices~$u_1,\, u_2, \, \ldots, u_m$ for varying strike prices~$K_1, \, K_2, \, \ldots, K_m$, here corresponding to different values of $x'$. Once we can extrapolate $u$ for extreme values of $x'$, we would know the entire time-zero profile of $u$.

>>>>

\subsection{Homogeneity of the solution}
First, we assume that the payoff function $\phi$ now depends on a parameter~$x' > 0$ (i.e., $\phi = \phi(x;x')$).  The motivation for this is that in the case of a European put or call, $x'$ represents the strike price. Furthermore, we assume that $\phi$ is homogeneous of degree one in~$x$ and $x'$. That is, we assume
$$
	\phi(\beta x; \beta x') = \beta \phi(x;x').
$$ 
Note that standard put and call payoffs satisfy this assumption. We show that the option price function~$v$ is homogeneous of degree one in~$x$ and $x'$. That is, we want to show for $v = v(x,t; x')$ that
		\begin{equation}
			\label{eqn:homogen}
			v(\beta x, t; \beta x') = \beta v(x,t; x')
		\end{equation}
for all $\beta > 0$. This equality can be proven via a uniqueness argument as follows. We first express \eqref{eqn:PIDE} as $\mathscr{L} v = 0$. Now let $w = w(x,t; x')$ solve the following final value problem:
		\begin{align}
			\label{eqn:subPIDE}
			\begin{split}
			&\mathscr{L}w = 0, \qquad w(x,T; x') = \beta\phi(x;x').
			\end{split}
		\end{align}
Next, we define the function $v_1(x,t;x') = \beta v(x,t;x')$, where $v$ is a solution to (\ref{eqn:PIDE}), (\ref{eqn:PIDEcondition}). Then
	\begin{align*}
		\mathscr{L}v_1 = \beta \mathscr{L}v = 0.
	\end{align*}
For the terminal condition, since $v(x,T;x') = \phi(x;x')$, this implies that
	\begin{equation*}
		v_1(x,T;x') = \beta v(x,T; x') = \beta\phi(x;x').
	\end{equation*}
Therefore $v_1$ satisfies the final value problem \eqref{eqn:subPIDE}. On the other hand, we now let $v_2(x,t,x') = v(\beta x, t; \beta x')$. Computing the derivatives gives
	\begin{equation*}
		\fr{\pr v_2}{\pr x} = \beta D_1v, \quad \fr{\pr^2 v_2}{\pr x^2} = \beta^2 D_{11}v,
	\end{equation*}
where $D_1$ and $D_{11}$ represent the first and second partial derivatives with respect to the first argument, respectively. Substituting these into (\ref{eqn:subPIDE}), we get
	\begin{align*}
		\mathscr{L}v_2 = \mathscr{L}v = 0,
	\end{align*}
and by the homogeneity of $\phi$, the terminal condition is
	\begin{align*}
		v_2(x,T;x') = v\left( \beta x, T; \beta x' \right) = \phi(\beta x; \beta x') = \beta \phi(x;x').
	\end{align*}
Hence $v_2$ also satisfies the final value problem \eqref{eqn:subPIDE}. By uniqueness, we have
	\begin{equation*}
		v\left(\beta x, t; \beta x'\right) = v_2(x,t;x') = v_1(x,t;x') = \beta v(x,t;x'),
	\end{equation*}
thus proving the homogeneity property for $v$ and any general payoff $\phi$ that is homogeneous of degree one in~$x$ and $x'$.

@@

\section{Implied volatility formula}
From (\ref{eqn:DupireLike}) and (\ref{eqn:DupireCond}), it is possible to now solve the inverse problem of implied volatility estimation. Throughout the remainder of this section, we will assume that~$r$ and $q$ are constants. Suppose that we are given $u(x',0;S_0)$ for all $x' > 0$. We wish to derive an explicit formula for $\sigma$ in terms of certain integrals of $u$ with respect to $x'$. The reason for this is that in practice one can observe different time-zero option prices~$u_1,\, u_2, \, \ldots, u_m$ for varying strike prices~$K_1, \, K_2, \, \ldots, K_m$, here corresponding to different values of $x'$. Once we can extrapolate $u$ for extreme values of $x'$, we would know the entire time-zero profile of $u$.
